Population Differentiation Analysis

### 2017-09-07 doc/RMD/pop-diff.Rmd
attempt to adjust legend width in DAPC fig

```{r dapc-region-dualplot, fig.width = 13, fig.height = 6}
LEG <- cowplot::get_legend(LDS_PLOT + theme(legend.position = "right") + theme(legend.text = element_text(size = 12)))
cowplot::plot_grid(LEG,
                   LDS_PLOT + 
                     theme(legend.position = "none") +
                     theme(plot.margin = unit(c(0, 0, 0, 0), "lines")) +
                     theme(panel.border = element_rect(color = "grey50")) +
                     theme(aspect.ratio = 0.935), 
                   REGION_PLOT +
                     theme(plot.margin = unit(c(0, 1, 0, 0), "lines")), 
                   nrow = 1, 
                   rel_widths = c(0.25, 0.75, 1),
                   label_size = 25,
                   label_fontfamily = "Helvetica",
                   labels = c(NA, "A", "B"),
                   align = "v",
                   axis = "t")
cowplot::ggsave(filename = file.path(PROJHOME, "results/figures/publication/DAPC.pdf"),
       width = 13,
       height = 6
      )
```

>>>>

```{r dapc-region-dualplot, fig.width = 13, fig.height = 6}
LEG <- cowplot::get_legend(LDS_PLOT + 
                             theme(legend.position = "right") + 
                             theme(legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "lines")) +
                             theme(legend.text = element_text(size = 12)))
cowplot::plot_grid(LEG,
                   LDS_PLOT + 
                     theme(legend.position = "none") +
                     theme(plot.margin = unit(c(0, 0, 0, 0), "lines")) +
                     theme(panel.border = element_rect(color = "grey50")) +
                     theme(aspect.ratio = 0.935), 
                   REGION_PLOT +
                     theme(plot.margin = unit(c(0, 1, 0, 0), "lines")), 
                   nrow = 1, 
                   rel_widths = c(0.25, 0.75, 1),
                   label_size = 25,
                   label_fontfamily = "Helvetica",
                   labels = c(NA, "A", "B"),
                   align = "v",
                   axis = "t")
cowplot::ggsave(filename = file.path(PROJHOME, "results/figures/publication/DAPC.pdf"),
       width = 13,
       height = 6
      )
```
